### 2004-07-20 Documentation/Manual.tex
Changes Meeting P+W made

\input{tumlogo}

\begin{minipage}{7cm}
\begin{center}
{\bf Technische Universit{\"a}t M{\"u}nchen} \\
Physik-Department \\
Institut f{\"u}r Theoretische Physik, T30d \\
\end{center}
\end{minipage}

\vspace{-2cm}

\hfill \oTUM{3.5cm}

\vspace{3cm}

\begin{center}
{ \Large \bf
\GLOBES\ 1.X \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and experiment definition manual }

@@

\begin{center}
{\large Patrick Huber, Manfred Lindner, Walter Winter}
\end{center}

@@

\GLOBES\ is mainly developed for academic use. Thus The \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the following reference
\begin{quote}
P. Huber, M. Lindner and W. Winter ... 
\end{quote}
and \emph{not} this manual. This manual does not constitute a scientific 
publication and will not be submitted to any scientific journal. 
It will evolve during time since it is intendend for 
regular revision.
Besides, many of the data which is used by \GLOBES\ and distributed together
with it should be correctly referenced where possible. For details see the
???.

Apart from that, \GLOBES\ is free software and open source, as such it is 
licensed under the GNU Public License.

@@

\bibliographystyle{./unsrt}
\bibliography{references}

>>>>

\vspace*{1.5cm}

\begin{center}
{ \Large \bf
{\Huge \GLOBES\ 2.0} \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and experiment definition manual }

@@

\vspace{0.5cm}

\begin{center}
{\large Patrick Huber$^a$, Manfred Lindner$^b$, Walter Winter$^c$}
\end{center}

\vspace{0.3cm}

\begin{center}

Current affiliation(s):

\vspace*{0.5cm}

{\em $^{\mathrm{a},\mathrm{b},\mathrm{c}}$%
       Institut f\"ur Theoretische Physik, Physik--Department,\\
       Technische Universit\"at M\"unchen,
       James--Franck--Strasse, D--85748 Garching, Germany}

\end{center}

@@

\subsection*{Referencing the \GLOBES\ software}

\GLOBES\ is developed for academic use. Thus, the \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the reference~\cite{globes_paper}
\begin{quote}
P. Huber, M. Lindner and W. Winter ... 
\end{quote}
but \emph{not} this manual. This manual itself is not scientific 
publication and will not be submitted to a scientific journal. 
It will evolve during time since it is intended for 
regular revision. Besides that, many of the data which are used by \GLOBES\ and distributed together with it should be properly referenced. 
For details see below.

Apart from that, \GLOBES\ is free software and open source, \ie, it is 
licensed under the GNU Public License.

\subsection*{Referencing the data in \GLOBES}
\label{ref_data}

\index{norm}{Referencing!data in \GLOBES}
\GLOBES\ wouldn't be useful without having high quality input data.
Much of these input data have been published elsewhere and the authors
of those publications would appreciate to be cited whenever their work
is used. It is solely the user's responsibility 
to make sure that he understands where the input material for \GLOBES\ comes
from and if additional work has to be cited in addition to the 
\GLOBES\ paper~\cite{globes_paper}. To assist with this task, we provide  the necessary information for the data coming along together with \GLOBES.

When using the built-in Earth matter density profile, the 
original source is \Ref~\cite{Stacey}.

All files ending with \verb+.dat+ or \verb+.glb+ 
in the \verb+data+ subdirectory of the \GLOBES\ tar-ball have on top a comment field which clearly indicates which works should be
cited when using a certain file. Make sure that dependencies are correctly
tracked, \ie , in some cases files included by other files need to be 
checked, too (for example, cross section or flux files). One can use 
the \verb+-v3+ option to \verb+globes+ to see which files
are included.

It is recommended that you use the same style for your own input files, since, in case they are distributed, everbody will know how to correctly reference your work.

@@

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{./unsrt}
\bibliography{references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
